---
title: "2024-10-22_ko-heatmap-clusters"
format:
  html:
    embed-resources: true
editor: visual
title-block-banner: true
fig-cap-location: top
---

## ATF4 / CEBPG KO heatmaps, cluster-specific gOST Plots, and gene lists

### Version 1 and 2: Filter for DEGS in 1) **(DMSO vs Halo) and/or (KO vs Rosa) conditions** or 2) **(KO vs Rosa) conditions only**, then cluster the data by (KO vs Rosa) conditions only

```{r}
#| echo: false
#| output: false

# Load packages and data
here::i_am("output/reports/2024-10-22_ko-heatmap-clusters.qmd")
library(here)
library(gprofiler2)

ko_only_heatmap <- readRDS(here("output", "objects", "s05_ko_only_heatmap.rds"))
ko_halo_heatmap <- readRDS(here("output", "objects", "s05_ko_halo_heatmap.rds"))
ko_halo2_heatmap <- readRDS(here("output", "objects", "s05_ko_halo2_heatmap.rds"))

gostplots_ko_halo <- readRDS(here("output", "objects", "s05_ko_halo_gostplots.rds"))
gostplots_ko_only <- readRDS(here("output", "objects", "s05_ko_only_gostplots.rds"))
gostplots_ko_halo2 <- readRDS(here("output", "objects", "s05_ko_halo2_gostplots.rds"))

clust_genes_ko_halo <- readRDS(here("output", "objects", "s05_ko_halo_gostplots_clust_genes.rds"))
clust_genes_ko_only <- readRDS(here("output", "objects", "s05_ko_only_gostplots_clust_genes.rds"))
clust_genes_ko_halo2 <- readRDS(here("output", "objects", "s05_ko_halo2_gostplots_clust_genes.rds"))


```

##### Heatmaps

```{r}
#| layout-ncol: 2
#| fig-width: 5
#| fig-height: 10
#| fig-cap:
#|   - "DEGs from (Halo vs DMSO) or (KO vs Rosa) conditions"
#|   - "Only DEGs from (KO vs Rosa) conditions"
ko_halo_heatmap
ko_only_heatmap

```

##### gOST plots

```{r}
#| layout-ncol: 2

htmltools::tagList(gostplots_ko_halo)

htmltools::tagList(gostplots_ko_only)

```

##### Gene lists

```{r}
#| layout-ncol: 2
print(clust_genes_ko_halo)
print(clust_genes_ko_only)
```


### Version 3: Filter for DEGS in **(DMSO vs Halo) and/or (KO vs Rosa) conditions** then cluster the data by all conditions, including the effect of Halo vs. DMSO

##### Heatmaps

```{r}
#| fig-width: 5
#| fig-height: 10
ko_halo2_heatmap
```


##### gOST plots

```{r}
htmltools::tagList(gostplots_ko_halo2)
```

##### Gene lists

```{r}
print(clust_genes_ko_halo2)
```
